Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2024-07-04 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
expertise paper

\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%

@@

@@

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Title here},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}

@@

@@

  \title{Title here}
      \cortext[cor1]{Corresponding author}

  \begin{abstract}
  The text of your abstract. 150 -- 250 words.
  \end{abstract}
    \begin{keyword}
    key \sep dictionary \sep 
    word
  \end{keyword}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{fitness-trackers-as-a-method-to-assess-hr-as-an-indicator-of-stress}{%
\subsection{Fitness Trackers as a Method to Assess HR as an Indicator of
Stress}\label{fitness-trackers-as-a-method-to-assess-hr-as-an-indicator-of-stress}}

@@

\hypertarget{teacher-stress-and-important-resources}{%
\subsection{Teacher Stress and Important
Resources}\label{teacher-stress-and-important-resources}}

@@

\hypertarget{hr-in-teaching-learning-contexts}{%
\subsection{HR in Teaching-Learning
Contexts}\label{hr-in-teaching-learning-contexts}}

@@

\hypertarget{present-study}{%
\subsection{Present Study}\label{present-study}}

@@

\begin{verbatim}
## New names:
## * `` -> `...6`
## * `` -> `...7`
## * `` -> `...8`
## * `` -> `...9`
## * `` -> `...10`
## * `` -> `...11`
\end{verbatim}

\begin{verbatim}
## Warning in left_join(main, df_merge, by = "ID"): Detected an unexpected many-to-many relationship between `x` and `y`.
## i Row 1 of `x` matches multiple rows in `y`.
## i Row 1 of `y` matches multiple rows in `x`.
## i If a many-to-many relationship is expected, set `relationship =
##   "many-to-many"` to silence this warning.
\end{verbatim}

\begin{verbatim}
## function (..., type = "latex", title = "", style = "default", 
##     summary = NULL, out = NULL, out.header = FALSE, column.labels = NULL, 
##     column.separate = NULL, covariate.labels = NULL, dep.var.caption = NULL, 
##     dep.var.labels = NULL, dep.var.labels.include = TRUE, align = FALSE, 
##     coef = NULL, se = NULL, t = NULL, p = NULL, t.auto = TRUE, 
##     p.auto = TRUE, ci = FALSE, ci.custom = NULL, ci.level = 0.95, 
##     ci.separator = NULL, add.lines = NULL, apply.coef = NULL, 
##     apply.se = NULL, apply.t = NULL, apply.p = NULL, apply.ci = NULL, 
##     colnames = NULL, column.sep.width = "5pt", decimal.mark = NULL, 
##     df = TRUE, digit.separate = NULL, digit.separator = NULL, 
##     digits = NULL, digits.extra = NULL, flip = FALSE, float = TRUE, 
##     float.env = "table", font.size = NULL, header = TRUE, initial.zero = NULL, 
##     intercept.bottom = TRUE, intercept.top = FALSE, keep = NULL, 
##     keep.stat = NULL, label = "", model.names = NULL, model.numbers = NULL, 
##     multicolumn = TRUE, no.space = NULL, notes = NULL, notes.align = NULL, 
##     notes.append = TRUE, notes.label = NULL, object.names = FALSE, 
##     omit = NULL, omit.labels = NULL, omit.stat = NULL, omit.summary.stat = NULL, 
##     omit.table.layout = NULL, omit.yes.no = c("Yes", "No"), order = NULL, 
##     ord.intercepts = FALSE, perl = FALSE, report = NULL, rownames = NULL, 
##     rq.se = "nid", selection.equation = FALSE, single.row = FALSE, 
##     star.char = NULL, star.cutoffs = NULL, suppress.errors = FALSE, 
##     table.layout = NULL, table.placement = "!htbp", zero.component = FALSE, 
##     summary.logical = TRUE, summary.stat = NULL, nobs = TRUE, 
##     mean.sd = TRUE, min.max = TRUE, median = FALSE, iqr = FALSE) 
## {
##     save.warn.option <- getOption("warn")
##     options(warn = -1)
##     return(.stargazer.wrap(..., type = type, title = title, style = style, 
##         summary = summary, out = out, out.header = out.header, 
##         column.labels = column.labels, column.separate = column.separate, 
##         covariate.labels = covariate.labels, dep.var.caption = dep.var.caption, 
##         dep.var.labels = dep.var.labels, dep.var.labels.include = dep.var.labels.include, 
##         align = align, coef = coef, se = se, t = t, p = p, t.auto = t.auto, 
##         p.auto = p.auto, ci = ci, ci.custom = ci.custom, ci.level = ci.level, 
##         ci.separator = ci.separator, add.lines = add.lines, apply.coef = apply.coef, 
##         apply.se = apply.se, apply.t = apply.t, apply.p = apply.p, 
##         apply.ci = apply.ci, colnames = colnames, column.sep.width = column.sep.width, 
##         decimal.mark = decimal.mark, df = df, digit.separate = digit.separate, 
##         digit.separator = digit.separator, digits = digits, digits.extra = digits.extra, 
##         flip = flip, float = float, float.env = float.env, font.size = font.size, 
##         header = header, initial.zero = initial.zero, intercept.bottom = intercept.bottom, 
##         intercept.top = intercept.top, keep = keep, keep.stat = keep.stat, 
##         label = label, model.names = model.names, model.numbers = model.numbers, 
##         multicolumn = multicolumn, no.space = no.space, notes = notes, 
##         notes.align = notes.align, notes.append = notes.append, 
##         notes.label = notes.label, object.names = object.names, 
##         omit = omit, omit.labels = omit.labels, omit.stat = omit.stat, 
##         omit.summary.stat = omit.summary.stat, omit.table.layout = omit.table.layout, 
##         omit.yes.no = omit.yes.no, order = order, ord.intercepts = ord.intercepts, 
##         perl = perl, report = report, rownames = rownames, rq.se = rq.se, 
##         selection.equation = selection.equation, single.row = single.row, 
##         star.char = star.char, star.cutoffs = star.cutoffs, suppress.errors = suppress.errors, 
##         table.layout = table.layout, table.placement = table.placement, 
##         zero.component = zero.component, summary.logical = summary.logical, 
##         summary.stat = summary.stat, nobs = nobs, mean.sd = mean.sd, 
##         min.max = min.max, median = median, iqr = iqr, warn = save.warn.option))
## }
## <bytecode: 0x000001fa06756810>
## <environment: namespace:stargazer>
\end{verbatim}

\hypertarget{method}{%
\section{Method}\label{method}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

@@

\hypertarget{setting-and-procedure}{%
\subsection{Setting and Procedure}\label{setting-and-procedure}}

@@

\hypertarget{measures}{%
\subsection{Measures}\label{measures}}

\hypertarget{heart-rate-data-and-heart-rate-intervals}{%
\subsubsection{Heart Rate Data and Heart Rate
Intervals}\label{heart-rate-data-and-heart-rate-intervals}}

@@

\hypertarget{teaching-experience}{%
\subsubsection{Teaching Experience}\label{teaching-experience}}

@@

\hypertarget{subjective-appraisal-of-the-classroom-events-and-coping-processes}{%
\subsubsection{Subjective appraisal of the classroom events and coping
processes}\label{subjective-appraisal-of-the-classroom-events-and-coping-processes}}

@@

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

@@

Regarding the teachers' HR trend, we displayed the HR trend over the
course of the entire study. For z-standardization as a method to account
for individual differences in the baseline HR, we visually compared
unstandardized and standardized mean HR trends for the entire two-hours
study. For testing Hypothesis 1a, which examined the HR levels in the
different intervals, we initially conducted a one-way ANOVA with
repeated measures as an omnibus test. The dependent variable comprised
the standardized HR mean for each interval. To identify the highest HR
level, we subsequently conducted t-tests with planned contrasts as
post-hoc tests, accompanied by the effect size d \citep{cohen1988new}.
Specifically, we tested the differences between the teaching interval
(\(I_2\)) and the other four intervals. Note that mean HR was calculated
at the subject level of \(n\) = 81 participants (see Table 1), whereas
the mean slope and mean intercept estimates are based on all values at
all measurement time points (see Table 2). For testing Hypothesis 1b,
which examined the HR changes within each interval, we conducted a
linear estimation of the increase or decrease in HR over time. To this
end, we used fixed intercept fixed slope regression models
\citep{gelman2006data} for each interval to estimate intercepts and
linear slopes for all individuals which were then averaged across
individuals\footnote{Although this procedure does not account for
  nonmonotonic progressions in individual HR, a graphical evaluation
  revealed that the linear estimates corresponded well to the majority
  of the cases (see XX in the supplementary material).}.

@@

>>>>

\documentclass[preprint, 3p,
authoryear]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%

@@

  \journal{Computers \& Education} % Sets Journal name

@@

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

\setcounter{secnumdepth}{5}
% Pandoc toggle for numbering sections (defaults to be off)

@@

\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{booktabs}

@@

  \title{New approaches to teachers' experience of stress: Do heart rate
measurements with fitness trackers provide an efficient, inexpensive,
and robust measurement method?}
    \author[Leipzig University]{Mandy Klatt%
  \corref{cor1}%
  \fnref{1}}
   \ead{mandy.klatt@uni-leipzig.de} 
    \author[Leipzig University]{Peer Keßler%
  %
  \fnref{2}}
   \ead{Peer@example.com} 
    \author[Leipzig University, Max Planck Institute for Evolutionary
Anthropology]{Gregor Kachel%
  %
  \fnref{1}}
   \ead{gregor@example.com} 
    \author[Leipzig University]{Christin Lotz%
  %
  \fnref{1}}
   \ead{christin@example.com} 
    \author[Leipzig University]{Anne Deiglmayr%
  %
  \fnref{3}}
   \ead{anne@example.com} 
      \affiliation[Leipzig University]{
    organization={Empirische Schul- und
Unterrichtsforschung},addressline={Marschnerstr.
29},city={Leipzig},postcode={4109},state={Sachsen},country={Germany},}
    \affiliation[Max Planck Institute for Evolutionary Anthropology]{
    organization={Department},addressline={Deutscher Pl.
6},city={Leipzig},postcode={4103},state={Sachsen},country={Germany},}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{ConceptualizationWriting - Original Draft
PreparationWriting - Review \& Editing}
    \fntext[2]{Writing - Original Draft PreparationWriting - Review \&
Editing}
    \fntext[3]{Supervision}

  \begin{abstract}
  One or two sentences providing a \textbf{basic introduction} to the
  field, comprehensible to a scientist in any discipline.

  Two to three sentences of \textbf{more detailed background},
  comprehensible to scientists in related disciplines.

  One sentence clearly stating the \textbf{general problem} being
  addressed by this particular study.

  One sentence summarizing the main result (with the words
  ``\textbf{here we show}'' or their equivalent).

  Two or three sentences explaining what the \textbf{main result}
  reveals in direct comparison to what was thought to be the case
  previously, or how the main result adds to previous knowledge.

  One or two sentences to put the results into a more \textbf{general
  context}.

  Two or three sentences to provide a \textbf{broader perspective},
  readily comprehensible to a scientist in any discipline.

  XXX In this proof-of-concept study, we aimed to advance the field of
  teacher stress by collecting heart rate data with wrist-worn devices
  and testing a methodology that has the potential to provide more
  insights on the non-invasive assessment of teacher stress. XXX
  \end{abstract}
    \begin{keyword}
    heart rate \sep photoplethysmography \sep wearable electronic
device \sep 
    teaching
  \end{keyword}

@@

\section{Introduction}\label{introduction}

@@

\subsection{Fitness Trackers as a Method to Assess HR as an Indicator of
Stress}\label{fitness-trackers-as-a-method-to-assess-hr-as-an-indicator-of-stress}

@@

\subsection{Teacher Stress and Important
Resources}\label{teacher-stress-and-important-resources}

@@

\subsection{HR in Teaching-Learning
Contexts}\label{hr-in-teaching-learning-contexts}

@@

\subsection{Present Study}\label{present-study}

@@

\section{Method}\label{method}

\subsection{Participants}\label{participants}

@@

\subsection{Setting and Procedure}\label{setting-and-procedure}

@@

\subsection{Measures}\label{measures}

\subsubsection{Heart Rate Data and Heart Rate
Intervals}\label{heart-rate-data-and-heart-rate-intervals}

@@

\subsubsection{Teaching Experience}\label{teaching-experience}

@@

\subsubsection{Subjective appraisal of the classroom events and coping
processes}\label{subjective-appraisal-of-the-classroom-events-and-coping-processes}

@@

\subsection{Data analysis}\label{data-analysis}

@@

Regarding the teachers' HR trend, we displayed the HR trend over the
course of the entire study. For z-standardization as a method to account
for individual differences in the baseline HR, we visually compared
unstandardized and standardized mean HR trends for the entire two-hours
study{[}\^{}3{]}. For all further analyses, we used standardized rather
than unstandardized HR values. {[}\^{}3{]}: Note that the study exceeded
the planned duration of two hours for a few participants. To avoid
distortions when mapping the HR over the course of the study (see Fig.
3), the endpoint was set at two hours for all participants, even though
data from later time points was used in the \emph{end interval} for a
few participants.

For testing Hypothesis 1a, which examined the HR levels in the different
intervals, we initially conducted a one-way ANOVA with repeated measures
as an omnibus test. The dependent variable comprised the standardized HR
mean for each interval. To identify the highest HR level, we
subsequently conducted t-tests with planned contrasts as post-hoc tests,
accompanied by the effect size d \citep{cohen1988new}. Specifically, we
tested the differences between the teaching interval (\(I_2\)) and the
other four intervals. Note that mean HR was calculated at the subject
level of \(n\) = 81 participants (see Table 1), whereas the mean slope
and mean intercept estimates are based on all values at all measurement
time points (see Table 2). For testing Hypothesis 1b, which examined the
HR changes within each interval, we conducted a linear estimation of the
increase or decrease in HR over time. To this end, we used fixed
intercept fixed slope regression models \citep{gelman2006data} for each
interval to estimate intercepts and linear slopes for all individuals
which were then averaged across individuals\footnote{Although this
  procedure does not account for nonmonotonic progressions in individual
  HR, a graphical evaluation revealed that the linear estimates
  corresponded well to the majority of the cases (see XX in the
  supplementary material).}.

@@

\section{Results}\label{results}

\subsection{Research goal 1: Mapping teachers' HR over the course of the
study
phases}\label{research-goal-1-mapping-teachers-hr-over-the-course-of-the-study-phases}

The first part of our first research goal was to map participants'
overall HR trend and explore whether z-standardization of participants'
HR is a useful method to account for individual differences in the
baseline HR. Means, standard deviations, and range of teachers'
unstandardized and standardized HR are shown in Table 1. Fig. 3 a. and
b. display the unstandardized and standardized HR trends, respectively.
HR initially increased, peaked, and then decreased, with the
unstandardized and standardized HR graphs showing high similarity. Thus,
for all further analyses, we used participants' standardized HR values.

\input{tab_1.tex}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/loess_plot_std_unstd_new.pdf}
  \caption{Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
  \label{Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
\end{figure}

### 2024-07-04 02_paper/02_study/02_eye tracking video questionnaire paper/paper_methods.Rmd
expertise paper

library(needs)

needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable,
      DescTools,
      formattable)

@@

XXX FRANZI 
```{r reaction_codingsystem, include=TRUE, echo=FALSE, results='asis'}

audit_table <- structure(
  list(
    Description = c(
      "The teacher reacts exclusively non-verbally to a disturbance. The flow of the lesson is not interrupted.",
      "The teacher reacts nonverbally and simultaneously with a short verbal reaction. The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixing gaze). The verbal response includes name calling, brief verbal prompts / admonitions.",
      "The teacher responds briefly and verbally to a disruption without a preceding nonverbal response.",
      "The teacher responds nonverbally and simultaneously overlapping with a verbal long response to a disruption. The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixating gaze).",
      "There is no reaction from the teacher to a disruption because the teacher does not consider it relevant to address the disruption. This information can only be obtained through the Stimulated Recall Interview.",
      "There is no reaction to a disruption on the part of the teacher because the teacher has not registered the disruption. This information can only be obtained through the Stimulated Recall Interview.",
      "Dysfunctional Response: the teacher responds inappropriately to a disruption through a lengthy verbal discussion of class rules, yelling around, etc."
                  ),
    `1` = c("Never", "1–2", "Never"),
    `2` = c("Monthly or less", "3-4", "Less than monthly"),
    `3` = c("2-4 times per month", "5-6", "monthly"),
    `4` = c("2-3 times per week","7-9", "Weekly"),
    `5` = c("4+ times per week", "10+", "Daily or almost daily"),
    `6` = c("bla"),
    `7` = c("bla")
          ),
  class = "data.frame",
  row.names = c(NA)
)

apa_table(
  audit_table,
  caption = "AUDIT-C scoring table",
  align = c("m{8cm}", rep("m{2cm}", 5)),
  col_spanners = list("Code" = c(2,7)),
  note = "Item scores are summed. Women who score 3+ and men who score 4+ are at-risk",
  landscape = TRUE
  )

@@

```{r presence_questionnaire, include=TRUE, echo=FALSE, results='asis'}
# load data files
quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  mutate(Group = ifelse(LI06_05 < 200, "Novice","Expert")) %>%
  dplyr::select(Group, LM01_01:LO01_02)

# create two data frames
quest.data.novice <- quest.data %>% filter(Group == "Novice")
quest.data.expert <- quest.data %>% filter(Group == "Expert")

# creating a matrix
quest.table.novice <- matrix(data = NA, nrow = 4, ncol = 8)
rownames(quest.table.novice) <- c("LM", "LB", "LP", "LV")
  colnames(quest.table.novice) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")

@@

loop.data <- quest.data.novice %>%
  dplyr::select(starts_with(match = i))

quest.table.novice[i, "N Items"] <- length(loop.data)

# calculating mean
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  mean() %>%
  round(., digits = 2) ->
quest.table.novice[i, "M"]

# calculating SD
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  sd() %>%
  round(., digits = 2) ->
quest.table.novice[i, "SD"]

# calculating Min
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  min() %>%
  round(., digits = 2) ->
quest.table.novice[i, "Min"]

# calculating Max
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  max() %>%
  round(., digits = 2) ->
quest.table.novice[i, "Max"]

# calculating Skewness
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  skewness() %>%
  round(., digits = 2) ->
quest.table.novice[i, "Skewness"]

# calculating Kurtosis
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  kurtosis() %>%
  round(., digits = 2) ->
quest.table.novice[i, "Kurtosis"]

quest.table.novice[i, "alpha"] <- round(alpha$alpha,2)

@@

# rename columns
rownames(quest.table.novice) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")

# format and insert table in manuscript
papaja::apa_table(
quest.table.novice,
  caption = "Scale analysis for novices' self-assessment",
  # note = "Write Note here",
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

# creating a matrix
quest.table.expert <- matrix(data = NA, nrow = 4, ncol = 8)
rownames(quest.table.expert) <- c("LM", "LB", "LP", "LV")
  colnames(quest.table.expert) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")

# creating a loop
# i <- "LM"

loop.data <- quest.data.expert %>%
  dplyr::select(starts_with(match = i))

quest.table.expert[i, "N Items"] <- length(loop.data)

# calculating mean
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  mean() %>%
  round(., digits = 2) ->
quest.table.expert[i, "M"]

# calculating SD
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  sd() %>%
  round(., digits = 2) ->
quest.table.expert[i, "SD"]

# calculating Min
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  min() %>%
  round(., digits = 2) ->
quest.table.expert[i, "Min"]

# calculating Max
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  max() %>%
  round(., digits = 2) ->
quest.table.expert[i, "Max"]

# calculating Skewness
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  skewness() %>%
  round(., digits = 2) ->
quest.table.expert[i, "Skewness"]

# calculating Kurtosis
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  kurtosis() %>%
  round(., digits = 2) ->
quest.table.expert[i, "Kurtosis"]

quest.table.expert[i, "alpha"] <- round(alpha$alpha,2)

# rename columns
rownames(quest.table.expert) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")

# format and insert table in manuscript
papaja::apa_table(
quest.table.expert,
  caption = "Scale analysis for experts' self-assessment",
  # note = "Write Note here",
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

```
XXX FRANZI
```{r item_analysis_classroom_management_novice, echo=FALSE, include=FALSE, results='asis'}
quest.data %>%
  dplyr::filter(Group == "Novice") %>% 
  dplyr::select(contains("LM")) %>%
  as.data.frame() %>%
  tab_itemscale(CSS = list(
    css.firsttablerow.col7 = "'cronbachs alpha';"
  ))
```

```{r item_analysis_classroom_management_expert, echo=FALSE, include=FALSE, results='asis'}
quest.data %>%
  dplyr::filter(Group == "Expert") %>% 
  dplyr::select(contains("LM")) %>%
  as.data.frame() %>%
  tab_itemscale(CSS = list(
    css.firsttablerow.col7 = "'cronbachs alpha';"
  ))
```

```{r item_analysis_balance_novice, echo=FALSE, include=FALSE, results='asis'}
quest.data %>%
  dplyr::filter(Group == "Novice") %>% 
  dplyr::select(contains("LB")) %>%
  as.data.frame() %>%
  tab_itemscale()
```

```{r item_analysis_balance_expert, echo=FALSE, include=FALSE, results='asis'}
quest.data %>%
  dplyr::filter(Group == "Expert") %>%
  dplyr::select(contains("LB")) %>%
  as.data.frame() %>%
  tab_itemscale()
```

```{r item_analysis_presence_novice, echo=FALSE, include=FALSE,results='asis'}
quest.data %>%
  dplyr::filter(Group == "Novice") %>%
  dplyr::select(contains("LP")) %>%
  as.data.frame() %>%
  tab_itemscale()
```

```{r item_analysis_presence_expert, echo=FALSE, include=FALSE,results='asis'}
quest.data %>%
  dplyr::filter(Group == "Expert") %>%
  dplyr::select(contains("LP")) %>%
  as.data.frame() %>%
  tab_itemscale()
```

```{r item_analysis_behavior_novice, echo=FALSE, include=FALSE,results='asis'}
quest.data %>%
  dplyr::filter(Group == "Novice") %>%
  dplyr::select(contains("LV")) %>%
  as.data.frame() %>%
  tab_itemscale()
```

```{r item_analysis_behavior_expert, echo=FALSE, include=FALSE,results='asis'}
quest.data %>%
  dplyr::filter(Group == "Expert") %>%
  dplyr::select(contains("LV")) %>%
  as.data.frame() %>%
  tab_itemscale()
```

>>>>

library(needs)
needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable,
      DescTools,
      formattable,
      psych)

@@

```{r reaction_codingsystem, include=TRUE, echo=FALSE, results='asis'}
# audit_table <- structure(
#   list(
#     Description = c(
#       "The teacher reacts exclusively non-verbally to a disturbance. The flow of the lesson is not interrupted.",
#       "The teacher reacts nonverbally and simultaneously with a short verbal reaction. The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixing gaze). The verbal response includes name calling, brief verbal prompts / admonitions.",
#       "The teacher responds briefly and verbally to a disruption without a preceding nonverbal response.",
#       "The teacher responds nonverbally and simultaneously overlapping with a verbal long response to a disruption. The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixating gaze).",
#       "There is no reaction from the teacher to a disruption because the teacher does not consider it relevant to address the disruption. This information can only be obtained through the Stimulated Recall Interview.",
#       "There is no reaction to a disruption on the part of the teacher because the teacher has not registered the disruption. This information can only be obtained through the Stimulated Recall Interview.",
#       "Dysfunctional Response: the teacher responds inappropriately to a disruption through a lengthy verbal discussion of class rules, yelling around, etc."
#                   ),
#     `1` = c("Never", "1–2", "Never"),
#     `2` = c("Monthly or less", "3-4", "Less than monthly"),
#     `3` = c("2-4 times per month", "5-6", "monthly"),
#     `4` = c("2-3 times per week","7-9", "Weekly"),
#     `5` = c("4+ times per week", "10+", "Daily or almost daily"),
#     `6` = c("bla"),
#     `7` = c("bla")
#           ),
#   class = "data.frame",
#   row.names = c(NA)
# )
# 
# apa_table(
#   audit_table,
#   caption = "AUDIT-C scoring table",
#   align = c("m{8cm}", rep("m{2cm}", 5)),
#   col_spanners = list("Code" = c(2,7)),
#   note = "Item scores are summed. Women who score 3+ and men who score 4+ are at-risk",
#   landscape = TRUE
#   )

@@

Bilanz:
LB01_01	Bilanz: Die Lernenden haben in dieser Unterrichtslektion etwas dazu gelernt.
LB01_02	Bilanz: Die Lernenden haben sich in dieser Unterrichtslektion wohl gefühlt.
LB01_03	Bilanz: Mediennutzung und Sozialformen waren dem Inhalt und der Situation der Unterrichtslektion angemessen.

Klassenmanagement:
LM01_01	Klassenmanagement: Die gesamte Unterrichtslektion wurde für den Lernstoff verwendet.
LM01_02	Klassenmanagement: Ich habe alles mitbekommen, was in der Klasse passiert ist.
LM01_03	Klassenmanagement: Den Lernenden war jederzeit klar, was sie tun sollten.
LM01_04	Klassenmanagement: Die Lernenden konnten ungestört arbeiten.
LM01_05	Klassenmanagement: Die Lernenden waren die ganze Unterrichtslektion über aktiv bei der Sache.
LM01_06	Klassenmanagement: Ich habe vieles mit kurzen Blicken und knappen Gesten geregelt.
LM01_07	Klassenmanagement: Auf Störungen habe ich angemessen reagiert.
LM01_08	Klassenmanagement: Bei Störungen gab ich den Lernenden ein klares STOP-Signal.

Redeanteil:
LO01_01	Redeanteil: Wieviel Prozent der gesamten Unterrichtslektion hat nach Ihrer Schätzung Ihr eigener Redeanteil eingenommen? ... %
LO01_02	Redeanteil: Wenn ich Fragen oder Aufgaben gestellt habe, habe ich den Lernenden folgende Zeit (in Sekunden) zum Nachdenken gegeben ... Sekunden

Präsenz:
LP01_01	Präsenzindikatoren: Ich hatte eine aufrechte, der Klasse zugewandte Körperhaltung.
LP01_02	Präsenzindikatoren: Ich habe den Lernenden direkt in die Augen geschaut.
LP01_03	Präsenzindikatoren: Ich habe meine Position im Raum bewusst eingesetzt und variiert.
LP01_04	Präsenzindikatoren: Ich habe alle oft angesehen.
LP01_05	Präsenzindikatoren: Meine Artikulation, Lautstärke und Tonhöhe waren angemessen.
LP01_06	Präsenzindikatoren: Meine Sprechgeschwindigkeit und Sprechpausen waren angemessen.
LP01_07	Präsenzindikatoren: Mein Sprechanteil an der gesamten Sprechzeit der Unterrichtslektion war angemessen.
LP01_08	Präsenzindikatoren: Meine Gestik und Mimik waren abwechslungsreich und ausdrucksstark.

Natürliches Verhalten:
LV01_01	Natürliches Verhalten: Während der Unterrichtslektion habe ich mich sehr natürlich verhalten.
LV01_02	Natürliches Verhalten: Es war für mich kein Problem, vor einer fiktiven Klasse zu unterrichten.
LV01_03	Natürliches Verhalten: Beim Unterrichten vor einer fiktiven Klasse habe ich mich so verhalten, wie ich es auch in der Schule tun würde.

```{r presence_questionnaire, include=TRUE, echo=FALSE, results='asis'}

# load data files
quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  dplyr::select(LI06_05, 
                LB01_01:LB01_03,
                LM01_01:LM01_08,
                LP01_01:LP01_08,
                LV01_01:LV01_03)

# creating a matrix
quest.table <- matrix(data = NA, nrow = 4, ncol = 8)
rownames(quest.table) <- c("LM", "LB", "LP", "LV")
colnames(quest.table) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","Alpha")

@@

loop.data <- quest.data %>%
  dplyr::select(starts_with(match = i))

quest.table[i, "N Items"] <- length(loop.data)

# calculating mean
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  mean() %>%
  round(., digits = 2) ->
quest.table[i, "M"]

# calculating SD
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  sd() %>%
  round(., digits = 2) ->
quest.table[i, "SD"]

# calculating Min
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  min() %>%
  round(., digits = 2) ->
quest.table[i, "Min"]

# calculating Max
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  max() %>%
  round(., digits = 2) ->
quest.table[i, "Max"]

# calculating Skewness
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  skewness() %>%
  round(., digits = 2) ->
quest.table[i, "Skewness"]

# calculating Kurtosis
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  kurtosis() %>%
  round(., digits = 2) ->
quest.table[i, "Kurtosis"]

# calculating Alpha
alpha <- loop.data %>%
  cronbach.alpha()

quest.table[i, "Alpha"] <- round(alpha$alpha,2)

@@

# rename columns
rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")

# format and insert table in manuscript
papaja::apa_table(
quest.table,
  caption = "Scale analysis for teachers' self-assessment",
  # note = "Write Note here",
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

```{r item_analysis_classroom_management, echo=FALSE, include=FALSE, results='asis'}
quest.data %>%
  dplyr::select(contains("LM")) %>%
  as.data.frame() %>%
  tab_itemscale(CSS = list(
    css.firsttablerow.col7 = "'cronbachs alpha';"
  ))
```

```{r item_analysis_balance, echo=FALSE, include=FALSE, results='asis'}
quest.data %>%
  dplyr::select(contains("LB")) %>%
  as.data.frame() %>%
  tab_itemscale()
```

```{r item_analysis_presence, echo=FALSE, include=FALSE,results='asis'}
quest.data %>%
  dplyr::select(contains("LP")) %>%
  as.data.frame() %>%
  tab_itemscale()
```

```{r item_analysis_behavior, echo=FALSE, include=FALSE,results='asis'}
quest.data %>%
  dplyr::select(contains("LV")) %>%
  as.data.frame() %>%
  tab_itemscale()
```
